Title here

### 2016-08-22 portfolio/text/ms.Rmd
Early draft of abstract, other text

```{r set-knitr-options, cache=FALSE, echo=FALSE}
library("knitr")
opts_chunk$set(cache=TRUE, echo=FALSE, message=FALSE, autodep=TRUE,
  results='hide')
opts_chunk$set(warning=FALSE, message=FALSE, cache.path="../cache/",
  cache.lazy=TRUE)
```

```{r get-dat, cache=FALSE}
load("../data-generated/output-values.rda")
```

@@

>>>>

```{r set-knitr-options, cache=FALSE, echo=FALSE}
library("knitr")
opts_chunk$set(cache=TRUE, echo=FALSE, message=FALSE, autodep=TRUE,
  results='hide')
opts_chunk$set(warning=FALSE, message=FALSE, cache.path="../cache/",
  cache.lazy=TRUE)
```
```{r get-dat, cache=FALSE}
load("../data-generated/output-values.rda")
```

\noindent
Main message:
Diversified portfolios of fishing permits and species reduce risk for fishermen,
but changing species diversity can be risky, costly, and limited by regulations.

@@

<!-- Fishing is inherently risky and we have long-sought regulations and fishing behaviors that reduce this risk. --> 
<!-- The increasing the diversity of species fished has been proposed to reduce risk for fishermen -->

Individuals relying on natural resources as their primary source of income
often experience high levels of income-variability 
due to the combined effects of environmental and price variation. 
Fishing is a prime example and
recent work has sought to identify regulations and fishing behaviours 
that can reduce this variability. 
A top candidate has been that fishing higher levels of species diversity
decreases income variability, which is concerning 
given that some fishing regulations and market forces
may be increasingly promoting specialization. 
However, it is unknown if this species-diversity effect 
on income variability holds 
across multiple approaches to diversifying catch,
at the level of individual permit holders,
and across all fisheries. 
Here, we simultaneously estimate the effects of three 
methods of diversification for Alaskan fishery permit holders
on revenue and revenue variability:
(1) owning multiple permits, 
(2) owning permits that inherently fish higher species diversity, 
and (3) adjusting species diversity within the constraints of a permit.
We control for changes in effort and other 
residual effects through time.
We find that 
fishing an additional permit is associated with lower variability (~XX--XX%) 
and higher revenue,
fishing permits with higher species diversity reduces risk 
(XX--XX% per unit increase in Simpson's diversity index),
but that changing species diversity within a
permit's constraints has a fishery-dependent effect on revenue and 
is usually (XX%) associated with increased revenue variability.
Our results suggest that the benefit of species diversity
on reducing revenue variability 
is mostly an across-permit effect, not
a benefit that can be easily harnessed by an individual permit holder.
Effective methods of diversification --- 
purchasing additional permits or switching permits ---
is costly and often limited by regulations such as limited entry
programs and individual transferable quotas (ITQs).
Our results suggest ...

\bigskip
\noindent
Extra:

- there is often limited room for intentional diversification within a permit
- in fact, specializing can be profitable within some fisheries

<!-- Main message in 25 words or less: -->

<!-- Take 1: -->
<!-- - There is a trend towards specializing on single salmon permits in Alaska -->
<!-- - Diversified portfolios of fishing permits and species reduce risk, -->
<!--   but changing species diversity for an individual permit holder can be risky -->
<!-- - The types of diversity needed to reduce risk are often restricted by -->
<!--   cost and regulations -->

<!-- Take 2: -->
<!-- - The effect of species diversification on revenue and risk for fishermen -->
<!-- depends on the type of diversification and the fishery. -->

<!-- Introduction, Methods, Results, Discussion, Conclusion:
<!-- 600, 900, 500, 800, 200, -->

<!-- write out each paragraph’s main message in 15 words or less -->

<!-- circulate skeleton ... this is the time to fix problems with flow, -->
<!-- ideas/content, main message -->
